### 2016-12-09 R/ITHIM.Rmd
First shot at figure for Jonathan on Dec. 12

```{r rustBelt, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}

>>>>

```{r rustBelt, eval = TRUE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}

ITHIMListScenario <- lapply(ITHIMList, function(ithim) updateITHIM(ithim, parName = "muwt", parValue = ithim$parameters$muwt + 10*7))

deltaDALYList <- mapply(sumDALY, ITHIMList, ITHIMListScenario)

getDALY <- function( ITHIM ){
foo <- data.frame(lapply(ITHIM$parameters$GBD, function(x) x$M$daly + x$F$daly))
sum(foo[,names(foo) %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD")])
}

burdenList <- lapply(ITHIMList, getDALY)
foo <- data.frame(daly = unlist(burdenList), delta = deltaDALYList)
foo <- within(foo, {
  daly <- daly + delta
  delta <- -delta
  state <- names(burdenList)
})

foo <- subset(foo, state %in% c("WI", "MI","OH"))

D <- melt(foo)

cbPalette <- c("#0072B2", "#56B4E9", "#999999", "#E69F00", "#009E73", "#F0E442", "#D55E00", "#CC79A7")

p <- ggplot(D, aes(state, value/1e3, fill = variable))
p + geom_bar(stat= "identity") + scale_x_discrete(name="") + scale_y_continuous(name="Thousands of DALYs") + guides(fill=FALSE) + scale_fill_manual(values=cbPalette) + coord_cartesian(ylim = c(175, 600)) + theme(axis.text.y  = element_text(size = 16)) + theme(axis.text.x  = element_text(size = 16), axis.title.x  = element_text(size = 16)) + coord_flip()
